---
title: "csv import test"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

Testing here is to import a bunch of csv files into a single dataframe.

Note for this example the files in `data-test` had a header row added by hand, which the social security files don't have when downloaded. This would be tedious for all the data, but perhaps an answer would be to create a tibble with the names first and then ignore header on import and then bind them to it. Perhaps.


```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
```

```{r import}
# looks at a folder and gets files that have ".txt"
files <- list.files(path = "data-test", pattern = "*.txt", full.names = T)

df <- sapply(
    files,
    read_csv,
    simplify = FALSE,
    # this is because gender was coming in T/F
    col_types = cols(Gender = col_character())
  ) %>% 
  bind_rows(.id = "id") %>% 
  clean_names()

df %>% head()
```

clean up the id name and rename as year:

```{r clean}
names <- df %>% 
  # done with two mutates. There might be a cleaner way but it works.
  mutate(
    id = str_remove(id, "data-test/yob"),
    id = str_remove(id, ".txt")
  ) %>% 
  # rename id to year since that is what it is
  rename(
    year = id
  )

names %>% head()
```

checking years

```{r}
names %>% 
  count(year)
```

